\section{Meeting Abstracts}

\subsection{Oral}

\begin{etaremune}
\item
    \Me, \SWei, \NSaloor, \WZhu, \& \GBeroza\ (2022).
    Detecting converted seismic phases of Tonga deep earthquakes: insights from deep-learning methods.
    2022 AGU Fall Meeting, Chicago, IL, USA. ID: S52A-05.
\item
    \Me, \MChen, \JLi, \& \SWei\ (2021).
    A 3D Azimuthal Anisotropy Model Beneath the East Asia Continent and Western Pacific Subduction Zone.
    2021 AGU Fall Meeting, New Orleans, LA, USA. ID: S14B-01.
\end{etaremune}

\subsection{Poster}

\begin{etaremune}
\item
    \Me, \JLi, \MChen, \& \SWei\ (2021).
    PyFK: A Fast MPI and CUDA Accelerated Python Package for Calculating Synthetic Seismograms Based on the Frequencywavenumber Method.
    2021 AGU Fall Meeting, New Orleans, LA, USA. ID: S14B-01.
\item
    \Me, \MChen, \TZhou, \BWang, \& \YKim\ (2021).
    Full waveform inversion of the crust and upper mantle beneath the East Asia Continent and Western Pacific Subduction Zone.
    2021 EGU General Assembly, Online. ID: EGU21-13849.
\item
    \Me, \MChen, \TZhou, \BWang, \& \YKim\ (2020).
    Slab Thinning Controls the Distribution of Large Deep Intraslab Earthquakes in the Western Pacific Subduction Zones.
    2020 AGU Fall Meeting, Online. ID: T018-0021.
\item
    \Me, \MChen, \TZhou, \BWang, \& \YKim\ (2020).
    Towards a Refined 3D Model of the Western Pacific Slab to Investigate the Nature of Deep Earthquakes.
    2019 AGU Fall Meeting, San Francisco, CA, USA. ID: T21F-0384.
\end{etaremune}
