\section{Peer-reviewed Publications}
% AGU style: https://publications.agu.org/agu-grammar-and-style-guide/
\newcommand{\Revision}{\emph{under revision}}
\newcommand{\CS}{*} % corresponding author
\newcommand{\CF}{\textsuperscript{\#}} % co-first author

\begin{etaremune}
\item \Me, \SWei, \WZhu, \GBeroza, \YJie, \& \NSaloor\ (2024).
    Deep Learning for Deep Earthquakes: Insights from OBS Observations of the Tonga Subduction Zone. 
    \emph{Geophysical Journal International}, \emph{238}(2). 
    \DOI{10.1093/gji/ggae200}
\item \SLi, \JLi, \TFerrand, \TZhou, \MLv, \Me, \RMaguire, \GHan, \JuanLi, \XBao, \YJiang, \& \TBao\ (2022).
    Deep geophysical anomalies beneath the Changbaishan Volcano.
    \emph{Journal of Geophysical Research: Solid Earth}, \emph{128}(4). 
    \DOI{10.1029/2022JB025671}
\item \GMao, \TFerrand, \JLi, \BZhu, \Me, \& \MChen\ (2022).
Unsupervised machine learning reveals slab hydration variations from deep earthquake distributions beneath the northwest Pacific.
    \emph{Communications Earth \& Environment}, \emph{56}(2022). 
    \DOI{10.1038/s43247-022-00377-x}
\item \TZhou, \Me, \JLi, \& \MChen\ (2022).
Assessment of seismic tomographic models of the contiguous United States using intermediate-period 3-D wavefield simulation.
    \emph{Geophysical Journal International}, \emph{228}(2). 
    \DOI{10.1093/gji/ggab406}
\item \TZhou, \JLi, \Me, \GLi, \& \MChen\ (2021).
CUSRA2021: A Radially Anisotropic Model of the Contiguous US and surrounding regions by full‐waveform inversion.
    \emph{Journal of Geophysical Research: Solid Earth}, \emph{127}(8). 
    \DOI{10.1029/2021JB023893}
\item \JLi, \MChen, \KKoper, \TZhou, \Me, \SLi, \& \GLi (2021).
FastTrip: A Fast MPI‐Accelerated 1D Triplication Waveform Inversion Package for Constraining Mantle Transition Zone Discontinuities.
    \emph{Seismological Research Letters}, \emph{92}(4). 
    \DOI{10.1785/0220200475}
\end{etaremune}

\subsection*{Papers submitted/under revision}
\begin{etaremune}
\item \Me, \MChen, \SWei, \JLi, \TZhou, \BWang, \& \YKim\ (2023).
    EARA2024: A New Radially Anisotropic Seismic Velocity Model for the Crust and Upper Mantle beneath East Asia and Northwestern Pacific Subduction Zones.
    \emph{Under Review at Geophysical Journal International}. 
\end{etaremune}
